get number of farms

### 2021-04-02 workflow/predict_farm_numbers.Rmd
finalized loop

aq_info <- read_csv('/home/shares/clean-seafood/raw_data/FAO/production/CL_FI_COUNTRY_GROUPS.csv') %>% 
  clean_names() %>% 
  select(iso3_code, geo_region_group, continent_group, eco_class_group)

@@

aq_types <- raw %>% 
  filter(!is.na(n_farms)) %>% 
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms) %>% 
  group_by(continent_group, group) %>% 
  summarise(tonnes_per_farm = mean(tonnes_per_farm))
```

>>>>

continent_info <- read_csv('data/CL_FI_COUNTRY_GROUPS.csv') %>% 
  janitor::clean_names() %>% 
  select(iso3_code, geo_region_group, continent_group, eco_class_group)

@@
